---
title: "WfG Data Compilation"
author: "Eliza Fink"
date: "4/3/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(tidyverse)
library(sf)
library(units)
library(maptools)
library(spatstat)

setwd("C:/Users/Eliza Fink/Desktop/WfG 2022")
```

# Load Data Sources

```{r}
# maintenance records 2012 - 2018
visits12 <- read.csv("2012_full_data.csv")
# maintenance records 2019
visits19 <- read.csv("2019_full_data.csv")
# maintenance records 2020
visits20 <- read.csv("2020_full_data.csv")
```

# Calculate Co-variables

## From Maintenance and Well Data

see maint_data.R

```{r}
# combine all data into one data frmae
visits <- bind_rows(visits12, visits19, visits20)

# remove observations without missing date
visits <- visits[which(visits$activity_date != "" &
                         is.na(visits$activity_date) == FALSE),]

rm("visits12", "visits19", "visits20")
```

List of Wells

```{r}
visits$decom <- ifelse(visits$pump_fixed == "decommissioned" |
                         visits$pump_fixed == "Désactiver cette point d'eau", visits$activity_date, "")


```

Write CSV - add time_between and last_funct

```{r}
write.csv(visits, file = "1220maint.csv") 
# added last known functionality and time between in excel before reloading

#################################################################################
```

don't rerun above this point!

```{r}
visits <- read.csv("1220maint.csv")
```


wells

```{r}
#get rid of NA values for lat/long

# mode function
calcmode <- function(a) {  
  vector <- unique(a)  
  vector[which.max(tabulate(match(a, vector)))]  
} 

wells <- visits[which(!is.na(visits$Latitude) &
                         visits$Longitude > 0),]

wells$sous_prefecture <- str_to_lower(wells$sous_prefecture)
wells$prefecture <- str_to_lower(wells$prefecture)

wells <- wells %>% 
  group_by(well_ID) %>%
  summarise(
    total_visits = n(),
    first_visit = min(as_date(mdy(activity_date))),
    decom_date = min(as_date(mdy(decom))),
    last_date = max (as_date(mdy(activity_date))),
    Latitude = median(Latitude),
    Longitude = median(Longitude),
    prefecture = calcmode(prefecture),
    sous_prefecture = calcmode(sous_prefecture)
    )

```


2020 participating pumps
```{r}
participating <- read.csv("participating_2020.csv")

participating <- as_vector(participating[1])

wells$participating <- if_else(wells$well_ID %in% participating, TRUE, FALSE)
```



maintenance data

```{r}
# make activity date into date format

visits <- visits %>%
  mutate(
    activity_date = as_date(mdy(activity_date)),
    Year = year(activity_date)
  )


# calculate the sum and percentage of past breakdowns for each pump

sum_past_broken <- c()
percent_past_broken <- c()

for(i in 1:(dim(visits)[1])){
  this_id <- visits[i, "well_ID"]
  this_data <- visits[which(visits$well_ID == this_id),]
  past_data <- this_data[which(this_data$activity_date < visits[i, "activity_date"]),]
  sum_past_broken <- append(sum_past_broken, 
                            dim(past_data)[1] - sum(past_data$pump_working))
  percent_past_broken<- append(percent_past_broken, sum_past_broken[i] / dim(past_data)[1])
}


visits$sum_past_broken<- sum_past_broken
visits$percent_past_broken<- percent_past_broken
visits$percent_past_broken[is.na(visits$percent_past_broken)] <- 0

rm(list=c("sum_past_broken", "percent_past_broken", "this_data", "past_data", "i", "this_id"))


# payment

# if there was any payment mark true

visits$payment_YN <- if_else(visits$payment > 0, TRUE, FALSE, FALSE)

# pump types

visits$pump_type <- as_factor(tolower(visits$pump_type))

visits <- visits %>%
  mutate(
    pump_type = recode (
      pump_type, 
      'hpv_60_2000' = 'hpv_60',
      'india_mk_ii' = 'india_mark_2',
      'decommissioned' = 'other',
      'vergnet_hpv_60_meter' = 'hpv_60',
      'vergnet hpv 60 2000' = 'hpv_60',
      'vergnet hpv 60' = 'hpv_60',
      'decommissioned' = 'other',
      'autres' = 'other',
      'vergnet hpv 100' = 'hpv_100',
      'vergnet hydro india' = 'hydro_india',
      'electrique' = 'electric',
      'vergnet hpv 60/2000 compteur' = 'hpv_60',
      'pompe électrique solaire avec tour' = 'other',
      'india mark 2' = 'india_mark_2',
      'lifepump' = 'other',
    )
  )

visits$pump_type <- as_factor(if_else(visits$pump_type == "", "other", as.character(visits$pump_type)))

# follow up
# is the visit a follow up? 2020 only

visits$follow_up <- visits$service_visit_type == "Visite de suivi"

# eep moto
# was the vist conducted by the eep moto teams (hybrid motorcycle)

visits$eep_moto <- visits$team_number %in% c("EEP Moto 1", "eep_moto_1", 
                                             "eep_moto_2", "EEP Moto 2", "Animateur Moto 1")

# rapid response
# was the pump in the rapid response program?


# list of pumps enrolled in the program
rapid_pumps <- unique(visits[which(visits$service_visit_type == "rapid_response" |
                                     visits$service_visit_type == "Réponse rapide" ),"well_ID"])

# code all visits as rapid response if they are in the list of rapid response pumps between first date of program and end of 2020

visits$rapid <- visits$well_ID %in% rapid_pumps &
  visits$activity_date >= min(visits[which(visits$service_visit_type == "rapid_response"),"activity_date"])

# month factor

visits$month <- month(visits$activity_date, label = TRUE)
```

## Population data


```{r}

# load facebook population data
pop <- read.csv("pop_caf_fb.csv") #population in 2018

# transform wells to spatial datatype

wells.st <- st_as_sf(wells, coords = c("Longitude", "Latitude"), crs = 4326)%>%
  st_transform(crs = 32633)

# empty data frame to fill in loop
well_pop <- data.frame(well_ID = c(),
                       pop_1k = c(),
                       pop_3k = c())


# loop the population (2018) within 1 and 3 k of each well
for (i in 1:dim(wells.st)[1]) {

  # which ID are we looking at
  id <- wells.st$well_ID[i]
  lat <- wells$Latitude[i]
  lon <- wells$Longitude[i]
  
  # makes small data frame +/- .1 degree from the well to reduce calculations
  lil_pop <- pop[pop$Lat > lat - .1 &
                  pop$Lat < lat + .1 &
                  pop$Lon > lon - .1 &
                  pop$Lon < lon + .1, ]
  
  # transform to spatial
  lil_pop <- st_as_sf(lil_pop, coords = c("Lon", "Lat"), crs = 4326)%>%
    st_transform(crs = 32633)
  
  # calculate distance to each raster point to pump
  lil_pop$distance <- st_distance(lil_pop$geometry, wells.st$geometry[i])
  
  # distances we are interested in
  threekm <- 3000
  onekm <- 1000
  units(threekm) <- as_units("m")
  units(onekm) <- as_units("m")
  
  # sum raster points less than distances
  onekpop <- sum(lil_pop[lil_pop$distance < onekm,]$Population)
  threekpop <- sum(lil_pop[lil_pop$distance < threekm,]$Population)
  
  # bind to data frame
  add <- data.frame(well_ID = id,
                    pop_1k = onekpop,
                    pop_3k = threekpop)
  
  well_pop = bind_rows(well_pop, add)
  
}


```

make sure to calculate population growth correctly -- see excel file for correct transformations

see pop_check.R file

Population Growth Adjustment

based on World Bank growth information here: https://data.worldbank.org/indicator/SP.POP.GROW?locations=CF
```{r}

# population growth adjustment

grow13 = 1.002596476
grow14 = 1.003641339
grow15 = 1.006475158
grow16 = 1.009857841
grow17 = 1.012774835
grow18 = 1.015191175
grow19 = 1.016746616
grow20 = 1.017668450



well_pop1 <- well_pop[,1:2]
well_pop1 <- well_pop1 %>%
  rename(
    pop18 = pop_1k
  )

well_pop3 <- well_pop[,c(1,3)]
well_pop3 <- well_pop3 %>%
  rename(
    pop18 = pop_3k
  )

well_pop1 <- well_pop1 %>%
  mutate(
    pop19 = pop18 * grow19,
    pop20 = pop18 * grow19 * grow20,
    pop17 = pop18 / grow18,
    pop16 = pop18 / grow18 / grow17,
    pop15 = pop18 / grow18 / grow17 / grow16,
    pop14 = pop18 / grow18 / grow17 / grow16 / grow15,
    pop13 = pop18 / grow18 / grow17 / grow16 / grow15 / grow14,
    pop12 = pop18 / grow18 / grow17 / grow16 / grow15/ grow14 / grow13
  )

well_pop3 <- well_pop3 %>%
  mutate(
    pop19 = pop18 * grow19,
    pop20 = pop18 * grow19 * grow20,
    pop17 = pop18 / grow18,
    pop16 = pop18 / grow18 / grow17,
    pop15 = pop18 / grow18 / grow17 / grow16,
    pop14 = pop18 / grow18 / grow17 / grow16 / grow15,
    pop13 = pop18 / grow18 / grow17 / grow16 / grow15 / grow14,
    pop12 = pop18 / grow18 / grow17 / grow16 / grow15/ grow14 / grow13
  )

# pivot data frames

well_pop1 <- well_pop1 %>%
  rename(
    '2012' = 'pop12',
    '2013' = 'pop13',
    '2014' = 'pop14',
    '2015' = 'pop15',
    '2016' = 'pop16',
    '2017' = 'pop17',
    '2018' = 'pop18',
    '2019' = 'pop19',
    '2020' = 'pop20'
  )


well_pop1 <- well_pop1 %>%
  pivot_longer(c('2012','2013','2014','2015','2016','2017','2018','2019', '2020'), 
               names_to = "Year", values_to = "Population_1k")

well_pop3 <- well_pop3 %>%
  rename(
    '2012' = 'pop12',
    '2013' = 'pop13',
    '2014' = 'pop14',
    '2015' = 'pop15',
    '2016' = 'pop16',
    '2017' = 'pop17',
    '2018' = 'pop18',
    '2019' = 'pop19',
    '2020' = 'pop20'
  )

well_pop3 <- well_pop3 %>%
  pivot_longer(c('2012','2013','2014','2015','2016','2017','2018','2019','2020'), 
               names_to = "Year", values_to = "Population_3k")


pop_tot <- left_join(well_pop1, well_pop3)

write.csv(pop_tot, file = "pop.csv")

rm(list = c("lil_pop", "well_pop", "well_pop1", "well_pop3", "grow13", "grow14", "grow15", "grow16",
            "grow17", "grow18", "grow19", "grow20"))

```

Don't run above here for pop

```{r}
pop_wells <- read_csv("pop.csv", 
    col_types = cols(...1 = col_skip()))
```


## Spatial

```{r}
cities <- read.csv("CAR_cities.csv")
```


average distance to nearest 5 water for good wells

```{r}

# nearest neighbor
# well.spat (spatial) data frame will contain all spatial variables of wells
well.spat <- data.frame(
  well_ID = character(),
  Year = numeric(),
  average_nn = numeric()
)

#calculate nearest neighbor
for(i in 2012:2020){
  #make separate data frame for that year
  #get rid of wells not yet visited
  wellsyear <- wells.st[which(year(wells.st$first_visit) <= i),]
  #get rid of decommissioned wells
  wellsyear <- wellsyear[which(year(wellsyear$decom_date) >= i |
                                 is.na(wellsyear$decom_date) == TRUE),]
  
  wellsyear$Year <- i
  
  #change to spatial data frame object
  wellsyear.ppp <- as(wellsyear, "Spatial")
  #to ppp format, for use in spat stat
  wellsyear.ppp <- as(wellsyear.ppp, "ppp")
  
  #distance in meters to nearest neighbor
  wellsyear$dist1 <- nndist(wellsyear.ppp)
  #distance in meters to second nearest neighbor
  wellsyear$dist2 <- nndist(wellsyear.ppp, k = 2)
  #distance to third nearest neighbor
  wellsyear$dist3 <- nndist(wellsyear.ppp, k = 3)
  #calculate nearest neighbor estimates
  wellsyear$dist4 <- nndist(wellsyear.ppp, k = 4)
  #calculate nearest neighbor estimates
  wellsyear$dist5 <- nndist(wellsyear.ppp, k = 5)
  #calculate nearest neighbor estimates
  
  wellsyear <- wellsyear %>% mutate(
    average_nn = (dist1 + dist2 + dist3 + dist4 + dist5) / 5
  )
  
  wellsyear$geometry <- NULL
  
  
  wellsyear <- wellsyear[,c(1,9,15)]

  well.spat <- rbind(well.spat, wellsyear)
}

```

distance to water for good office
distance to nearest urban center

```{r}
# distance to headquarters AND distance to nearest urban center
##distance to office calculation
BanguiHQ <- cities[14,c(2:3)]
BerberatiHQ <- cities[15,c(2:3)]

BanguiHQ <- sf::st_as_sf(BanguiHQ, coords = c("Long", "Lat"), crs = 4326)
BerberatiHQ <- sf::st_as_sf(BerberatiHQ, coords = c("Long", "Lat"), crs = 4326)

wells.st <- sf::st_as_sf(wells, coords = c("Longitude", "Latitude"), crs = 4326)
# calculate distance to headquarters in meters
wells.st$dist_ban <- sf::st_distance(wells.st$geometry,BanguiHQ$geometry[1])
wells.st$dist_ber <- sf::st_distance(wells.st$geometry,BerberatiHQ$geometry[1])

wells.st$dist_office <- ifelse(wells.st$dist_ber < wells.st$dist_ban, 
                               wells.st$dist_ber / 1000, 
                               wells.st$dist_ban / 1000)

#distance to city calculation
cities.sf <- sf::st_as_sf(cities, coords = c("Long", "Lat"), crs = 4326)

bangui <- cities.sf[1,4]
bimbo <- cities.sf[2,4]
berberati <- cities.sf[3,4]
carnot <- cities.sf[4,4]
bambari <- cities.sf[5,4]
bouar <- cities.sf[6,4]
bassan <- cities.sf[7,4]
bria <- cities.sf[8,4]
nola <- cities.sf[9,4]
kaga <- cities.sf[10,4]
sibut <- cities.sf[11,4]
mbaiki <- cities.sf[12,4]
bozoum <- cities.sf[13,4]


wells.st <- wells.st %>%
  mutate(
    bangui = sf::st_distance(wells.st$geometry,bangui$geometry[1]),
    bimbo = sf::st_distance(wells.st$geometry,bimbo$geometry[1]),
    berberati = sf::st_distance(wells.st$geometry,berberati$geometry[1]),
    carnot = sf::st_distance(wells.st$geometry,carnot$geometry[1]),
    bambari = sf::st_distance(wells.st$geometry,bambari$geometry[1]),
    bouar = sf::st_distance(wells.st$geometry,bouar$geometry[1]),
    bassan = sf::st_distance(wells.st$geometry,bassan$geometry[1]),
    bria = sf::st_distance(wells.st$geometry,bria$geometry[1]),
    nola = sf::st_distance(wells.st$geometry,nola$geometry[1]),
    kaga = sf::st_distance(wells.st$geometry,kaga$geometry[1]),
    sibut = sf::st_distance(wells.st$geometry,sibut$geometry[1]),
    mbaiki = sf::st_distance(wells.st$geometry,mbaiki$geometry[1]),
    bozoum = sf::st_distance(wells.st$geometry,bozoum$geometry[1])
  )

wells.st <- wells.st %>%
  rowwise() %>%
  mutate(
    urban_center = min(bangui, bimbo, berberati, carnot, bambari, bouar, bassan,
                       bria, nola, kaga, sibut, mbaiki, bozoum)
  )

wells.st$urban_center <- wells.st$urban_center / 1000
wells.st$urban_center <- as.numeric(wells.st$urban_center)

distances <- wells.st[,c("well_ID", "participating", "dist_office", "urban_center")]

```


## Combine into one data frame


```{r}
full_data <- left_join(visits, distances)
full_data <- left_join(full_data, well.spat)
full_data <- left_join(full_data, pop_wells)
```
additional factors

```{r}
full_data$month <- factor(month(full_data$activity_date, label = TRUE, abbr = TRUE), ordered = FALSE)
####add factor for conflict
full_data$conflict <- full_data$Year %in% c(2013, 2014)
####add flipped payment outcome
####change nearest neighbor units to kilometers
full_data$average_nn <- full_data$average_nn / 1000
# now all distance units are in km

write.csv(full_data, file = "full_data.csv")
```

those to use in modeling

```{r}
model <- full_data[,c("well_ID","pump_fixed","pump_working", "payment_YN","activity_date",
                      "Year", "month", "time_between", "last_funct", "pump_type", "sum_past_broken", 
                      "percent_past_broken", "follow_up", "eep_moto", "rapid", "dist_office", 
                      "urban_center", "average_nn", "Population_1k", "Population_3k", "conflict",
                      "participating")]

model <- model[which(!apply(model, MARGIN = 1, function(x) sum(is.na(x))>0)),]

write.csv(model, file = "model.csv")
```

those in modeling including pref/sous-pref

```{r}
model_sp <- full_data[,c("well_ID","pump_fixed","pump_working", "payment_YN","activity_date",
                      "Year", "month", "time_between", "last_funct", "pump_type", "sum_past_broken", 
                      "percent_past_broken", "follow_up", "eep_moto", "rapid", "dist_office", 
                      "urban_center", "average_nn", "Population_1k", "Population_3k", "conflict",
                      "participating", "prefecture", "sous_prefecture")]

model_sp <- model_sp[which(!apply(model_sp, MARGIN = 1, function(x) sum(is.na(x))>0)),]

model_sp <- model_sp[which(model_sp$sous_prefecture != ""),]
model_sp$prefecture <- str_to_lower(model_sp$prefecture)
model_sp$sous_prefecture <- str_to_lower(model_sp$sous_prefecture)


clean_pre <- function(string) {
  string <- str_replace_all(string, "mambere kadei", "mamberekadei")
  string <- str_replace_all(string, "sanghambaere", "sangha-mbaéré")
  string <- str_replace_all(string, "ouham pende", "ouhampende")
  string <- str_replace_all(string, "nanamambere", "nana-mambere")
  string <- str_replace_all(string, "ombelampoko", "ombella m'poko")
  string <- str_replace_all(string, "ombella m poko", "ombella m'poko")
  string <- str_replace_all(string, "nana mambere", "nana-mambere")
  string <- str_replace_all(string, "mambéré kadeï", "mamberekadei")
  string <- str_replace_all(string, "membéré kadeï", "mamberekadei")
  string <- str_replace_all(string, "mambere kadeï", "mamberekadei")
  string <- str_replace_all(string, "ombela mpoko", "ombella m'poko")
  string <- str_replace_all(string, "sangha-mbaere", "sangha-mbaéré")
  string <- str_replace_all(string, "sangha-mba?r?", "sangha-mbaéré")
  string <- str_replace_all(string, "k?mo", "kemo")
  string <- str_replace_all(string, "sangha-mbaérééré", "sangha-mbaéré")
  string <- str_replace_all(string, "sangha mbaere", "sangha-mbaéré")
  string <- str_replace_all(string, "sangha-mbaéré?r?", "sangha-mbaéré")
  string <- str_replace_all(string, "nana-mamberei", "nana-mambere")
  string <- str_replace_all(string, "kekemo", "kemo")
  string <- str_replace_all(string, "k?kemo", "kemo")
  return(string)
}

model_sp$prefecture <- clean_pre(model_sp$prefecture)

model_sp$prefecture <- if_else(
  model_sp$prefecture == "kekemo" | model_sp$prefecture == "k?kemo", "kemo", model_sp$prefecture
)

model_sp$prefecture <- if_else(
  model_sp$prefecture == "sangha-mbaéré?r?", "sangha-mbaéré", model_sp$prefecture
)

model_sp$sous_prefecture <- if_else(model_sp$sous_prefecture == "berb?rati", "berberati", model_sp$sous_prefecture)
model_sp$sous_prefecture <- if_else(model_sp$sous_prefecture == "mba?ki", "mbaiki", model_sp$sous_prefecture)
model_sp$sous_prefecture <- if_else(model_sp$sous_prefecture == "amadagaza", "amada-gaza", model_sp$sous_prefecture)
model_sp$sous_prefecture <- if_else(model_sp$sous_prefecture == "sosso -nakombo", "sosso nakombo", model_sp$sous_prefecture)
model_sp$sous_prefecture <- if_else(model_sp$sous_prefecture == "d?d?dedemokouba", "dedemokouba", model_sp$sous_prefecture)
model_sp$sous_prefecture <- if_else(model_sp$sous_prefecture == "bossemt?le", "bossemtele", model_sp$sous_prefecture)
model_sp$sous_prefecture <- if_else(model_sp$sous_prefecture == "bossemb?le", "bossembele", model_sp$sous_prefecture)

clean_sp <- function(string) {
  string <- str_replace_all(string, "berb?rati", "berberati")
  string <- str_replace_all(string, "mba?ki", "mbaiki")
  string <- str_replace_all(string, "mbaïki", "mbaiki")
  string <- str_replace_all(string, "bossemptele", "bossemtele")
  string <- str_replace_all(string, "bossemt?le", "bossemtele")
  string <- str_replace_all(string, "ombella m poko", "ombella m'poko")
  string <- str_replace_all(string, "nana mambere", "nana-mambere")
  string <- str_replace_all(string, "dedemoukouba", "dedemokouba")
  string <- str_replace_all(string, "dede moukouba", "dedemokouba")
  string <- str_replace_all(string, "dede mokouba", "dedemokouba")
  string <- str_replace_all(string, "dede mokouba", "dedemokouba")
  string <- str_replace_all(string, "dede-mokouba", "dedemokouba")
  string <- str_replace_all(string, "d?d?-mokouba", "dedemokouba")
  string <- str_replace_all(string, "nana bakassa", "nanabakassa")
  string <- str_replace_all(string, "m'baïki", "mbaiki")
  string <- str_replace_all(string, "dédé mokouba", "dedemokouba")
  string <- str_replace_all(string, "berbérati", "berberati")
  string <- str_replace_all(string, "bérbérati", "berberati")
  string <- str_replace_all(string, "bibmbo", "bimbo")
  return(string)
}

model_sp$sous_prefecture <- clean_sp(model_sp$sous_prefecture)

write.csv(model_sp, file = "model_sp.csv")
```

