---
title: "sensitivity"
author: "Eliza Fink"
date: "4/14/2022"
output: html_document
---
# set up

```{r setup, include=FALSE}
# load packages

library(tidyverse)
library(lattice)
library(caret)
library(olsrr)
library(RCurl)
library(Matrix)
library(lme4)
library(sjPlot)
library(readxl)
```

load datasets

- model - full model
- breakdown - subset of model conditional on breakdown
- model_sp - subset of model with administrative data
- model_part - subset of model with participating pumps
- model_inst - subset of model that includes the date of installation

```{r}
# read in model data
setwd("C:/Users/Eliza Fink/Desktop/WfG 2022")

# data set excluding missing values (from "Data Compilation" RMarkdown)
# n = 16398
model <- read_csv("model.csv", col_types = cols(...1 = col_skip(), 
    activity_date = col_date(format = "%Y-%m-%d")))

# data set excluding missing values (from "Data Compilation" RMarkdown), but including sous-prefecture and prefecture
# n = 13406
model_sp <- read_csv("model_sp.csv", col_types = cols(...1 = col_skip(), 
    activity_date = col_date(format = "%Y-%m-%d")))

```
```{r}
#fix sous_prefecture typos

model_sp$sous_prefecture <- as_factor(if_else(as_factor(model_sp$sous_prefecture) == "mongoumba", 
                                              "moungoumba",
                                              if_else(as_factor(model_sp$sous_prefecture) == "ngaounday",
                                              "ngaoundaye", model_sp$sous_prefecture)))
```

pump type - add india mark 3 and 4 to india mark 2 and electric to other because they are too small of categories

```{r}
model <- model %>%
  mutate(
    pump_type = if_else(pump_type %in% c("india_mark_2", "india_mark_3", "india_mark_4"),
                        "india_mark", pump_type),
    pump_type = if_else(pump_type == "electric", "other", pump_type)
  )

model_sp <- model_sp %>%
  mutate(
    pump_type = if_else(pump_type %in% c("india_mark_2", "india_mark_3", "india_mark_4"),
                        "india_mark", pump_type),
    pump_type = if_else(pump_type == "electric", "other", pump_type)
  )
```

model conditional on breakdown
```{r}
breakdown <- model[which(model$pump_working == FALSE),]
# n = 3066
```

only pumps labeled as "participating" in 2020
```{r}
participating <- as_vector(read_csv("participating_2020.csv"))

model_part <- model[which(model$well_ID %in% participating),]
# n = 12297

breakdown_part <- model_part[which(model_part$pump_working == FALSE),]
```

model of only wells with installation data
```{r, warning = FALSE}
# data that has well installation information

# read in well installation dates

wells <- read_excel("C:/Users/Eliza Fink/Desktop/WfG 2021/Raw Data/wells 1-1-2012.xlsx", 
                             col_types = c("text", "skip", "skip", 
                                           "skip", "skip", "skip", "skip", "skip", 
                                           "skip", "numeric", "numeric", "date", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "numeric", 
                                           "numeric", "numeric", "text", "text", 
                                           "text", "numeric", "numeric", "numeric", 
                                           "numeric", "skip", "numeric", "text", 
                                           "text", "text", "text", "text"))

wells <- wells[,c("well_id", "install_date")]
wells <- rename(wells,  "well_ID" = "well_id")

model_inst <- left_join(model, wells)
model_inst <- model_inst[which(!is.na(model_inst$install_date)),]

```

# basic models

Models reported in body of paper
Full data sets and 

## working 

Predictor Variables:
  - Time since last maintenance visit
  - Hybrid Moto
  - Rapid Response
  - Distance to WfG office
  - Distance to Urban Center
  - Population
  - NN

```{r}
glmer_working <- glmer(pump_working ~ time_between + eep_moto +
                         rapid + dist_office + urban_center + 
                         Population_1k + 
                         average_nn + pump_type + follow_up +
                         (1 | well_ID),
                       data = model, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_working)

confusionMatrix(as_factor(predict(glmer_working, type="response") >= 0.5), 
                as_factor(model$pump_working))

save_table <- cbind(coef(summary(glmer_working)), confint(glmer_working, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/working_main.csv")

tab_model(glmer_working)
```


## fixed 

Predictor Variables:
  - Community payment
  - Time since last maintenance visit
  - Hybrid Moto
  - Rapid Response
  - Distance to WfG office
  - Distance to Urban Center
  - Population
  - NN
  
```{r}
glmer_fixed <- glmer(pump_fixed ~ time_between + eep_moto + payment_YN +
                         rapid + dist_office + urban_center +
                       Population_1k + follow_up + pump_type +
                         average_nn + (1 | well_ID),
                       data = breakdown, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_fixed)

confusionMatrix(as_factor(predict(glmer_fixed, type="response") >= 0.5), 
                as_factor(breakdown$pump_fixed))

save_table <- cbind(coef(summary(glmer_fixed)), confint(glmer_fixed, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/fixed_main.csv")

tab_model(glmer_fixed)
```

## payment

Predictor Variables:
  - Pump Working
  - Pump Fixed
  - Time since last maintenance visit
  - Hybrid Moto
  - Rapid Response
  - Distance to WfG office
  - Distance to Urban Center
  - Population
  - NN
  
```{r}
glmer_payment <- glmer(payment_YN ~ last_funct +
                         time_between +
                         eep_moto + pump_working + pump_fixed +
                         rapid + dist_office + urban_center + Population_1k +
                         average_nn + (1 | well_ID),
                       data = model, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_payment)

confusionMatrix(as_factor(predict(glmer_payment, type="response") >= 0.5), 
                as_factor(model$payment_YN))

save_table <- cbind(coef(summary(glmer_payment)), confint(glmer_payment, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/payment_main.csv")

tab_model(glmer_payment)
``` 

# with administrative sub-region data

## working

### prefecture

#### fixed effect
```{r}
glmer_working <- glmer(pump_working ~ time_between + eep_moto +
                         rapid + dist_office + urban_center + 
                         Population_1k + 
                         average_nn + pump_type + follow_up + prefecture +
                         (1 | well_ID),
                       data = model_sp, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_working)

confusionMatrix(as_factor(predict(glmer_working, type="response") >= 0.5), 
                as_factor(model_sp$pump_working))

save_table <- cbind(coef(summary(glmer_working)), confint(glmer_working, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/working_pref.csv")
```

#### random effect
```{r}
glmer_working <- glmer(pump_working ~ time_between + eep_moto +
                         rapid + dist_office + urban_center + 
                         Population_1k + 
                         average_nn + pump_type + follow_up + (1 | prefecture) +
                         (1 | well_ID),
                       data = model_sp, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_working)

confusionMatrix(as_factor(predict(glmer_working, type="response") >= 0.5), 
                as_factor(model_sp$pump_working))

save_table <- cbind(coef(summary(glmer_working)), confint(glmer_working, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/working_pref_r.csv")

tab_model(glmer_working)
```

### sous-prefecture

#### fixed effect
```{r}
glmer_working <- glmer(pump_working ~ time_between + eep_moto +
                         rapid + dist_office + urban_center + 
                         Population_1k + 
                         average_nn + pump_type + follow_up + sous_prefecture +
                         (1 | well_ID),
                       data = model_sp, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_working)

confusionMatrix(as_factor(predict(glmer_working, type="response") >= 0.5), 
                as_factor(model_sp$pump_working))

save_table <- cbind(coef(summary(glmer_working)), confint(glmer_working, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/working_sous.csv")
```

#### random effect

```{r}
glmer_working <- glmer(pump_working ~ time_between + eep_moto +
                         rapid + dist_office + urban_center + 
                         Population_1k + 
                         average_nn + pump_type + follow_up  + (1 | sous_prefecture) +
                         (1 | well_ID),
                       data = model_sp, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_working)

confusionMatrix(as_factor(predict(glmer_working, type="response") >= 0.5), 
                as_factor(model_sp$pump_working))

save_table <- cbind(coef(summary(glmer_working)), confint(glmer_working, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/working_sous_r.csv")

tab_model(glmer_working)
```

## fixed

### prefecture

#### fixed
```{r}
glmer_fixed <- glmer(pump_fixed ~ time_between + eep_moto + payment_YN +
                         rapid + dist_office + urban_center +
                       Population_1k + follow_up + pump_type +
                         average_nn + prefecture + (1 | well_ID),
                       data = model_sp[which(model_sp$pump_working == FALSE),], 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_fixed)

confusionMatrix(as_factor(predict(glmer_fixed, type="response") >= 0.5), 
                as_factor(model_sp[which(model_sp$pump_working == FALSE),]$pump_fixed))

save_table <- cbind(coef(summary(glmer_fixed)), confint(glmer_fixed, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/fixed_pref.csv")
```

#### random

```{r}
glmer_fixed <- glmer(pump_fixed ~ time_between + eep_moto + payment_YN +
                         rapid + dist_office + urban_center +
                       Population_1k + follow_up + pump_type +
                         average_nn + (1 | prefecture) + (1 | well_ID),
                       data = model_sp[which(model_sp$pump_working == FALSE),], 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_fixed)

confusionMatrix(as_factor(predict(glmer_fixed, type="response") >= 0.5), 
                as_factor(model_sp[which(model_sp$pump_working == FALSE),]$pump_fixed))

save_table <- cbind(coef(summary(glmer_fixed)), confint(glmer_fixed, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/fixed_pref_r.csv")

tab_model(glmer_fixed)
```

### sous-prefecture

#### fixed
```{r}
glmer_fixed <- glmer(pump_fixed ~ time_between + eep_moto + payment_YN +
                         rapid + dist_office + urban_center +
                       Population_1k + follow_up + pump_type +
                         average_nn + sous_prefecture + (1 | well_ID),
                       data = model_sp[which(model_sp$pump_working == FALSE),], 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_fixed)

confusionMatrix(as_factor(predict(glmer_fixed, type="response") >= 0.5), 
                as_factor(model_sp[which(model_sp$pump_working == FALSE),]$pump_fixed))

save_table <- cbind(coef(summary(glmer_fixed)), confint(glmer_fixed, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/fixed_sous.csv")
```
#### random

```{r}
glmer_fixed <- glmer(pump_fixed ~ time_between + eep_moto + payment_YN +
                         rapid + dist_office + urban_center +
                       Population_1k + follow_up + pump_type +
                         average_nn + (1 | sous_prefecture) + (1 | well_ID),
                       data = model_sp[which(model_sp$pump_working == FALSE),], 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_fixed)

confusionMatrix(as_factor(predict(glmer_fixed, type="response") >= 0.5), 
                as_factor(model_sp[which(model_sp$pump_working == FALSE),]$pump_fixed))

save_table <- cbind(coef(summary(glmer_fixed)), confint(glmer_fixed, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/fixed_sous_r.csv")

tab_model(glmer_fixed)
```

## payment

### prefecture

#### fixed
```{r}
glmer_payment <- glmer(payment_YN ~ last_funct +
                         time_between +
                         eep_moto + pump_working + pump_fixed +
                         rapid + dist_office + urban_center + Population_1k +
                         average_nn + prefecture + (1 | well_ID),
                       data = model_sp, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_payment)

confusionMatrix(as_factor(predict(glmer_payment, type="response") >= 0.5), 
                as_factor(model_sp$payment_YN))

save_table <- cbind(coef(summary(glmer_payment)), confint(glmer_payment, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/payment_pref.csv")
``` 
#### random

```{r}
glmer_payment <- glmer(payment_YN ~ last_funct +
                         time_between +
                         eep_moto + pump_working + pump_fixed +
                         rapid + dist_office + urban_center + Population_1k +
                         average_nn + (1 | prefecture) + (1 | well_ID),
                       data = model_sp, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_payment)

confusionMatrix(as_factor(predict(glmer_payment, type="response") >= 0.5), 
                as_factor(model_sp$payment_YN))

save_table <- cbind(coef(summary(glmer_payment)), confint(glmer_payment, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/payment_pref_r.csv")

tab_model(glmer_payment)
``` 

### sous-prefecture

#### fixed

```{r}
glmer_payment <- glmer(payment_YN ~ last_funct +
                         time_between +
                         eep_moto + pump_working + pump_fixed +
                         rapid + dist_office + urban_center + Population_1k +
                         average_nn + sous_prefecture + (1 | well_ID),
                       data = model_sp, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_payment)

confusionMatrix(as_factor(predict(glmer_payment, type="response") >= 0.5), 
                as_factor(model_sp$payment_YN))

save_table <- cbind(coef(summary(glmer_payment)), confint(glmer_payment, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/payment_sous.csv")
``` 

#### random

```{r}
glmer_payment <- glmer(payment_YN ~ last_funct +
                         time_between +
                         eep_moto + pump_working + pump_fixed +
                         rapid + dist_office + urban_center + Population_1k +
                         average_nn + (1 | sous_prefecture) + (1 | well_ID),
                       data = model_sp, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_payment)

confusionMatrix(as_factor(predict(glmer_payment, type="response") >= 0.5), 
                as_factor(model_sp$payment_YN))

save_table <- cbind(coef(summary(glmer_payment)), confint(glmer_payment, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/payment_sous_r.csv")

tab_model(glmer_payment)
``` 

# with excluding outliers

Screen for outliers
```{r}

# create mahalanobis scores (multidimensional distance from mean)
mahal <- mahalanobis(model[ , c("time_between",
                                "dist_office", "urban_center", "average_nn", "Population_1k")], 
                     colMeans(model[ , c("time_between",
                                "dist_office", "urban_center", "average_nn", "Population_1k")], na.rm = TRUE),
                     cov(model[ , c("time_between",
                                "dist_office", "urban_center", "average_nn", "Population_1k")], use="pairwise.complete.obs"))


# find cutoff for bad scores

cutoff = qchisq(1 - .001,ncol(model[ , c("time_between", "dist_office", 
                                         "urban_center", "average_nn", "Population_1k")]))

ncol(model[ , c("time_between","dist_office", "urban_center", "average_nn", "Population_1k")]) ##this is degrees of freedom (for chi squared not analysis)
cutoff

#find out how many observations are outliers
summary(mahal < cutoff)
#451 observations are outliers out of 16398, ~3%
#check later if removing these pumps changes things

# remove outliers
no_outliers <- subset(model, mahal < cutoff)
# no outliers, 15947 observations


# look at outliers
outliers <- subset(model, mahal > cutoff)
# 160 / 451 pumps not working 
# 109 / 451 pumps not fixed

```

## working

```{r}
glmer_working <- glmer(pump_working ~ time_between + eep_moto +
                         rapid + dist_office + urban_center + 
                         Population_1k + 
                         average_nn + pump_type + follow_up +
                         (1 | well_ID),
                       data = no_outliers, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_working)

confusionMatrix(as_factor(predict(glmer_working, type="response") >= 0.5), 
                as_factor(no_outliers$pump_working))

save_table <- cbind(coef(summary(glmer_working)), confint(glmer_working, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/working_noout.csv")
```

## fixed

```{r}
glmer_fixed <- glmer(pump_fixed ~ time_between + eep_moto + payment_YN +
                         rapid + dist_office + urban_center +
                       Population_1k + follow_up + pump_type +
                         average_nn + (1 | well_ID),
                       data = no_outliers[which(no_outliers$pump_working == FALSE),], 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_fixed)

confusionMatrix(as_factor(predict(glmer_fixed, type="response") >= 0.5), 
                as_factor(no_outliers[which(no_outliers$pump_working == FALSE),]$pump_fixed))

save_table <- cbind(coef(summary(glmer_fixed)), confint(glmer_fixed, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/fixed_noout.csv")
```

## payment

```{r}
glmer_payment <- glmer(payment_YN ~ last_funct +
                         time_between +
                         eep_moto + pump_working + pump_fixed +
                         rapid + dist_office + urban_center + Population_1k +
                         average_nn + (1 | well_ID),
                       data = no_outliers, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_payment)

confusionMatrix(as_factor(predict(glmer_payment, type="response") >= 0.5), 
                as_factor(no_outliers$payment_YN))

save_table <- cbind(coef(summary(glmer_payment)), confint(glmer_payment, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/payment_noout.csv")
``` 

# participating

## working

```{r}
glmer_working <- glmer(pump_working ~ time_between + eep_moto +
                         rapid + dist_office + urban_center + 
                         Population_1k + 
                         average_nn + pump_type + follow_up +
                         (1 | well_ID),
                       data = model_part, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_working)

confusionMatrix(as_factor(predict(glmer_working, type="response") >= 0.5), 
                as_factor(model_part$pump_working))

save_table <- cbind(coef(summary(glmer_working)), confint(glmer_working, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/working_part.csv")
```

## fixed

```{r}
glmer_fixed <- glmer(pump_fixed ~ time_between + eep_moto + payment_YN +
                         rapid + dist_office + urban_center +
                       Population_1k + follow_up + pump_type +
                         average_nn + (1 | well_ID),
                       data = breakdown_part, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_fixed)

confusionMatrix(as_factor(predict(glmer_fixed, type="response") >= 0.5), 
                as_factor(breakdown_part$pump_fixed))

save_table <- cbind(coef(summary(glmer_fixed)), confint(glmer_fixed, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/fixed_part.csv")
```

## payment

```{r}
glmer_payment <- glmer(payment_YN ~ last_funct +
                         time_between +
                         eep_moto + pump_working + pump_fixed +
                         rapid + dist_office + urban_center + Population_1k +
                         average_nn + (1 | well_ID),
                       data = model_part, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_payment)

confusionMatrix(as_factor(predict(glmer_payment, type="response") >= 0.5), 
                as_factor(model_part$payment_YN))

save_table <- cbind(coef(summary(glmer_payment)), confint(glmer_payment, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/payment_part.csv")
``` 

# well installation

## working

```{r}
glmer_working <- glmer(pump_working ~ time_between + eep_moto +
                         rapid + dist_office + urban_center + 
                         Population_1k + 
                         average_nn + pump_type + follow_up + 
                         + install_date +
                         (1 | well_ID),
                       data = model_inst, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_working)

confusionMatrix(as_factor(predict(glmer_working, type="response") >= 0.5), 
                as_factor(model_inst$pump_working))

save_table <- cbind(coef(summary(glmer_working)), confint(glmer_working, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/working_inst.csv")
```

## fixed

```{r}
glmer_fixed <- glmer(pump_fixed ~ time_between + eep_moto + payment_YN +
                         rapid + dist_office + urban_center +
                       Population_1k + follow_up + pump_type +
                         average_nn + install_date + (1 | well_ID),
                       data = model_inst[which(model_inst$pump_working == FALSE),], 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_fixed)

confusionMatrix(as_factor(predict(glmer_fixed, type="response") >= 0.5), 
                as_factor(model_inst[which(model_inst$pump_working == FALSE),]$pump_fixed))

save_table <- cbind(coef(summary(glmer_fixed)), confint(glmer_fixed, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/fixed_inst.csv")
```

## payment

```{r}
glmer_payment <- glmer(payment_YN ~ last_funct +
                         time_between +
                         eep_moto + pump_working + pump_fixed +
                         rapid + dist_office + urban_center + Population_1k +
                         average_nn + install_date + (1 | well_ID),
                       data = model_inst, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_payment)

confusionMatrix(as_factor(predict(glmer_payment, type="response") >= 0.5), 
                as_factor(model_inst$payment_YN))

save_table <- cbind(coef(summary(glmer_payment)), confint(glmer_payment, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/payment_inst.csv")
``` 

# time unit to years instead of days 

```{r}
model$time_bw_year <- model$time_between / 365
breakdown$time_bw_year <- breakdown$time_between / 365
```


## working

```{r}
glmer_working <- glmer(pump_working ~ time_bw_year + eep_moto +
                         rapid + dist_office + urban_center + 
                         Population_1k + 
                         average_nn + pump_type + follow_up +
                         (1 | well_ID),
                       data = model, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_working)

confusionMatrix(as_factor(predict(glmer_working, type="response") >= 0.5), 
                as_factor(model$pump_working))

save_table <- cbind(coef(summary(glmer_working)), confint(glmer_working, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/working_year.csv")
```

## fixed

```{r}
glmer_fixed <- glmer(pump_fixed ~ time_bw_year + eep_moto + payment_YN +
                         rapid + dist_office + urban_center +
                       Population_1k + follow_up + pump_type +
                         average_nn + (1 | well_ID),
                       data = breakdown, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_fixed)

confusionMatrix(as_factor(predict(glmer_fixed, type="response") >= 0.5), 
                as_factor(breakdown$pump_fixed))

save_table <- cbind(coef(summary(glmer_fixed)), confint(glmer_fixed, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/fixed_year.csv")
```

## payment

```{r}
glmer_payment <- glmer(payment_YN ~ last_funct +
                         time_bw_year +
                         eep_moto + pump_working + pump_fixed +
                         rapid + dist_office + urban_center + Population_1k +
                         average_nn + (1 | well_ID),
                       data = model, 
                       family = binomial(link = 'logit'),
                       control = glmerControl(optimizer = "bobyqa"),
                       nAGQ = 0)

summary(glmer_payment)

confusionMatrix(as_factor(predict(glmer_payment, type="response") >= 0.5), 
                as_factor(model$payment_YN))

save_table <- cbind(coef(summary(glmer_payment)), confint(glmer_payment, parm = 'beta_', method = 'Wald'))
write.csv(save_table, file = "model_outputs/payment_year.csv")
``` 
